---
title: "Power calculations"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Power

If we have two independent samples of size n, and we reject the two sample null hypothesis that $\mu_{1}= \mu_{2}$, then the power of the one-tailed test is equal to 1 − $\beta$ where

Here's a [link](http://statweb.stanford.edu/~susan/courses/s141/hopower.pdf) to a nice site with plots to gain a better understanding.

$df = 2n − 2$ and the noncentrality parameter takes the value $\delta = d\sqrt{n/2}$ where d is Cohen’s effect size $$d = \dfrac{\mu_2-\mu_1}{\sigma}$$

Assuming that the two populations have the same standard deviation $\sigma$ (homogeneity of variances):

```{r pressure, echo=FALSE}
n=5
tsample=2
sig.level=0.05
tside=1
delta=55
sd=31
df <- pmax(1e-07, n - 1) * tsample
```

So the calculation is to find the proportion of the *alternative* curve that exceeds the rejection region of the null. We find the rejection quantile of the *null* t-distirbuion that correspondes to an $\alpha$ of 0.05.
```{r}
rejection=qt(sig.level/tside, df, lower.tail = FALSE)
```

Then we compute the cumulative distribution of the *alternative* distribution that exceeds it. Here, ncp is the non-centrality parameter specifying the 'off-center' nature of the alternative as explained above, and df is 2n-2 By specifying lower tail = FALSE we compute everything to the RIGHT of the rejection region.

```{r}
pt(rejection, df, ncp = sqrt(n/tsample) * delta/sd, lower.tail = FALSE)
````


##Here plot the distribution of the alternative

```{r}
plot(density(rt(10000000,df=8,ncp = sqrt(n/tsample) * delta/sd)),xlim=c(0,10),main="Alternative vs Null, Rejection")
lines(density(rt(1000000,df=8)))
###ncp, or the non-centrality  parameter, is like the deviation of the 
abline(v=qt(sig.level/tside, df, lower.tail = FALSE),col="red")

```

Power (0.80) is the area of the alternative curve to the right of  the rejection line.

Fortunately, there is code for all of this!
```{r}

#PowerLVESV
power.t.test(n = 5, d = 55, sig.level = 0.05 ,sd=31,alternative="one.sided")

#SWmean
power.t.test(n = 15, d = 2.5, sig.level = 0.05 ,sd=2.6,alternative="one.sided")

##SW_Netherlands

power.t.test(n = 12,d = 2.6, sig.level = 0.05,sd=2.5,alternative="one.sided")
```

As you  can see it preserves confirms  everything you've computed, althouth the power is slightly  different for the SW Netherlands analysis.
