---
title: "Simulating from the Prior"
output:
  html_document:
    df_print: paged
    toc: no
  html_notebook: default
  workflowr::wflow_html:
    code_folding: show
    toc: no
editor_options:
  chunk_output_type: inline
---



From the paper:

```
The posterior distributions of the probability of death at 1 year associated with multivessel percutaneous coronary intervention (PCI) versus culprit-lesion-only PCI are shown and were obtained on the basis of a Bayesian beta-binomial model assuming independent, noninformative beta (0.01, 0.01) priors. Posterior 95% credible intervals for the probability of death at 1 year are 0.45 to 0.55 for culprit-lesion-only PCI and 0.52 to 0.62 for multivessel PCI.
```


The OR of dying (D) over living (L) in the single vs multivessel arm:

$${\displaystyle OR={\frac {D_{single}/L_{single}}{D_{multi}/L_{multi}}}\,,}$$

Let $N$ be the number of patients in the single vessel arm and $M$ be the number of patients in the multivessel arm, and let $x$ be the proportion of single vessel patients who die at 1 year and $y$ be the proportion of patients in the multivessel arm dead after one year. Then:

$${\displaystyle OR={\frac {D_{S}/H_{S}}{D_{M}/H_{M}}}\,={\frac {Nx/(N-Nx)}{My/(M-My)}}\,}$$

We see that the numbers in the trial, n and m, cancel out, and we are left with: 

$${\displaystyle OR={\frac {x_{single}/(1-x_{single})}{y_{multi}/(1-y_{multi})}}\,,}$$

where $x_{single}$ and $y_{multi}$ now represent the relative **proportions** of death in each arm of the trial respectively, similar to the framework of the correspondence authors. We can then assemble the prior of the log OR using the simulated quantities:

```{r}

probdeath.single=rbeta(100000,1,0.01,0.01)
problife.single=1-probdeath.single

probdeath.multi=rbeta(100000,1,0.01,.01)
problife.multi=1-probdeath.multi


logOR=log((probdeath.single/probdeath.multi)/(problife.single/problife.multi))



```

If we then do a histogram of the nonNA logOR2 in the range of -1,1, we can see that it is 'approximately uniform'
```{r}
hist(logOR[logOR!="NaN"],xlim=c(-1.5,1.5),breaks = 10000)
```

We see that part of the problem lies in the fact that when $x$ and $y$ are simulated $\beta(0.01,0.01)$, $x$ and $y$ are often $0 or 1$, 

```{r}

p=seq(0,1,by=0.001)
prior=dbeta(p,0.01,0.01)

plot(p,prior,type="l",ylab="Density",lty=1,lwd=3,xlab = expression(theta),main="Prior Probability of Death")
```

As you can see, a preponderance of the weight for the propotion is on 0 or 1, which means that $1-x$ will also often by $0$ or $1$, making the ratio undefined.

